### 2021-11-26 content/80.formal-definition.tex
aligned tex/md of formal definitions
.. to cover Reviewer 2 improvements

\begin{eqnarray*}
ROCrate(R)                                  & \models & Root(R) \land Mentions(R, R) \land hasPart(R, d) \land \\
                                            & & Mentions(R, d) \land DataEntity(d) \land \\
                                            & & Mentions(R, c) \land ContextualEntity(c) \\
\forall r \ Root(r)                         & \Rightarrow & Dataset(r) \land name(r, n) \land description(r, d) \land \\
                                            & &             datePublished(r, date) \land license(e, l) \\
\forall e \forall n \ name(e, n)            & \Rightarrow & Value(n) \\
\forall e \forall s \ description(e, s)     & \Rightarrow & Value(s) \\
\forall e \forall d \ datePublished(e, d)   & \Rightarrow & Value(d) \\
\forall e \forall l \ license(e, l)         & \Rightarrow & ContextualEntity(l) \\
DataEntity(e)                               & \equiv &      File(e) \oplus Dataset(e) \\
Entity(e)                                   & \equiv &      DataEntity(e) \lor ContextualEntity(e) \\
\forall e \ Entity(e)                       & \Rightarrow & Class(e) \\
Mentions(R, s)                              & \models &     Relation(s, p, e) \oplus Attribute(s,  p, l) \\
Relation(s, p, o)                           & \models &     Entity(s) \land Property(p) \land  Entity(o) \\
Attribute(s, p, v)                          & \models &     Entity(s) \land Property(p) \land Value(v) \\
Value(v)                                    & \equiv &      v \in \mathbb{R} \oplus v \in \mathbb{S}
\end{eqnarray*}

@@

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or both\footnote{
    \url{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html\#contextual-vs-data-entities}
}; and must be typed with at least one $Class(e)$.

@@

\begin{eqnarray*}
Property(p)         & \Rightarrow &     type(p, \texttt{<http://www.w3.org/2000/01/rdf-schema\#Property>})   \\
Class(c)            & \Rightarrow &     type(c, \texttt{<http://www.w3.org/2000/01/rdf-schema\#Class>})  \\
Dataset(d)          & \Rightarrow &     type(d, \texttt{<http://schema.org/Dataset>})   \\
File(f)             & \Rightarrow &     type(f, \texttt{<http://schema.org/MediaObject>})   \\
CreativeWork(e)     & \Rightarrow &     ContextualEntity(e) \land type(e, \texttt{<http://schema.org/CreativeWork>})  \\
hasPart(e, t)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/hasPart>}, t)    \\
name(e, n)          & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/name>}, n)  \\
description(e, s)   & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/description>}, s)   \\
datePublished(e, d) & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/datePublished>}, d) \\
license(e, l)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/license>}, l) \land CreativeWork(l) \\
type(e, t)          & \Rightarrow &     Relation(e, \texttt{<http://www.w3.org/1999/02/22-rdf-syntax-ns\#type>}, t) \\
                    & & \land Class(t)   \\
String(s)           & \equiv &          Value(s) \land  s \in \mathbb{S} \\
String(s)           & \Rightarrow &     Datatype(s, \texttt{<http://www.w3.org/2001/XMLSchema\#string>}) \\
Decimal(d)          & \equiv &          Value(d) \land  d \in \mathbb{R} \\
Decimal(d)          & \Rightarrow &     Datatype(d, \texttt{<http://www.w3.org/2001/XMLSchema\#decimal>}) \\
Relation(s,p,o)     & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land IRI(o) \\
Attribute(s,p,o)    & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land Literal(o) \\
\end{eqnarray*}

>>>>

\begin{eqnarray*}
ROCrate(R)                                  & \models & Root(R) \land Mentions(R, R) \land hasPart(R, d) \land \\
                                            & & Mentions(R, d) \land DataEntity(d) \land \\
                                            & & Mentions(R, c) \land ContextualEntity(c) \\
\forall r \ Root(r)                         & \Rightarrow & Dataset(r) \land name(r, n) \land description(r, d) \land \\
                                            & &             datePublished(r, date) \land license(e, l) \\
\forall e \forall n \ name(e, n)            & \Rightarrow & Value(n) \\
\forall e \forall s \ description(e, s)     & \Rightarrow & Value(s) \\
\forall e \forall d \ datePublished(e, d)   & \Rightarrow & Value(d) \\
\forall e \forall l \ license(e, l)         & \Rightarrow & ContextualEntity(l) \\
DataEntity(e)                               & \equiv &      File(e) \oplus Dataset(e) \\
Entity(e)                                   & \equiv &      DataEntity(e) \lor ContextualEntity(e) \\
\forall e \ Entity(e)                       & \Rightarrow & type(e, c) \land Class(e) \\
\forall e \ ContextualEntity(e)             & \Rightarrow & name(e, n)  \\
Mentions(R, s)                              & \models &     Relation(s, p, e) \oplus Attribute(s,  p, l) \\
Relation(s, p, o)                           & \models &     Entity(s) \land Property(p) \land  Entity(o) \\
Attribute(s, p, v)                          & \models &     Entity(s) \land Property(p) \land Value(v) \\
Value(v)                                    & \equiv &      v \in \mathbb{R} \oplus v \in \mathbb{S}
\end{eqnarray*}

@@

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or both\footnote{
    \url{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html\#contextual-vs-data-entities}
}. Any $Entity(e)$ must be typed with at least one $Class(c)$, and every $ContextualEntity(e)$ must also have a $name(e,n)$; this corresponds to expectations for any \emph{referenced contextual entity} (section \ref{sec:contextualentities}).

@@

\begin{eqnarray*}
Property(p)         & \Rightarrow &     type(p, \texttt{<http://www.w3.org/2000/01/rdf-schema\#Property>})   \\
Class(c)            & \Rightarrow &     type(c, \texttt{<http://www.w3.org/2000/01/rdf-schema\#Class>})  \\
Dataset(d)          & \Rightarrow &     type(d, \texttt{<http://schema.org/Dataset>})   \\
File(f)             & \Rightarrow &     type(f, \texttt{<http://schema.org/MediaObject>})   \\
ContextualEntity(e) & \Rightarrow &     type(f, \texttt{<http://schema.org/Thing>})   \\
CreativeWork(e)     & \Rightarrow &     ContextualEntity(e) \land type(e, \texttt{<http://schema.org/CreativeWork>})  \\
hasPart(e, t)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/hasPart>}, t)    \\
name(e, n)          & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/name>}, n)  \\
description(e, s)   & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/description>}, s)   \\
datePublished(e, d) & \Rightarrow &     Attribute(e, \texttt{<http://schema.org/datePublished>}, d) \\
license(e, l)       & \Rightarrow &     Relation(e, \texttt{<http://schema.org/license>}, l) \land CreativeWork(l) \\
type(e, t)          & \Rightarrow &     Relation(e, \texttt{<http://www.w3.org/1999/02/22-rdf-syntax-ns\#type>}, t) \\
                    & & \land Class(t)   \\
String(s)           & \equiv &          Value(s) \land  s \in \mathbb{S} \\
String(s)           & \Rightarrow &     Datatype(s, \texttt{<http://www.w3.org/2001/XMLSchema\#string>}) \\
Decimal(d)          & \equiv &          Value(d) \land  d \in \mathbb{R} \\
Decimal(d)          & \Rightarrow &     Datatype(d, \texttt{<http://www.w3.org/2001/XMLSchema\#decimal>}) \\
Relation(s,p,o)     & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land IRI(o) \\
Attribute(s,p,o)    & \Rightarrow &     Triple(s,p,o) \land IRI(s) \land Literal(o) \\
\end{eqnarray*}
